---
title: "NCHS"
author: "Sanmi"
date: "5/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Goal: To download the complete dataset, clean and split into subsets for downstream analyses.

```{r message=FALSE, warning=FALSE}
rm(list = ls())
library(readr)
library(plyr)
library(dplyr)
library(survey)
library(srvyr)



```


```{r message=FALSE, warning=FALSE}

dat16<- read_csv("2016NSCHTopical_DRCv3_Sep2018.csv")
dat17_18<- read_csv("2017-2018 NSCH_Topical_DRC_Dec 2019.csv")
dat19_20<- read_csv("2019-2020 NSCH_Topical_CAHMI_DRC.csv")

```


### For each year, adjust the weights so that the dataset can be combined
```{r message=FALSE, warning=FALSE}

dat16$FWC_adj<-dat16$FWC/5
dat17_18$FWC_adj<-(dat17_18$FWC_1718*2)/5
dat19_20$FWC_adj<-(dat19_20$fwc_1920*2)/5

```

### Select variables from each year
```{r message=FALSE, warning=FALSE}

dat19_20b<-dat19_20%>%
  select(             HHID,FIPSST,STRATUM,
                      instype_1920,
                        SC_AGE_YEARS,
                       SC_SEX,
                        SC_RACE_R,
                        #   sc_race_ethnic_16to20,
               famstruct5_1920,
               contains("fpl"),
               HHLANGUAGE,
               FAMCOUNT,
               # Child Health Complexity Variables
               HCABILITY,
               HCEXTENT,
               ATHOMEHC,
               ARRANGEHC,
               K4Q22_R,
               K4Q23,
               K4Q24_R,
               K4Q36,
               K4Q01,
               K4Q02_R,
               HOSPITALER,
               K4Q20R,
               BREATHING,
               SWALLOWING,
               STOMACH,
               BLINDNESS,
               K2Q43B,
               PHYSICALPAIN,
               # maybe not use
               HANDS,
               COORDINATION,
               MEMORYCOND,
               WALKSTAIRS,
               DRESSING,
               # other predictors
               C4Q04,
               K5Q20_R,
               K5Q21,
               K8Q35,
               K2Q05,
               MOMAGE,
               StopCutWork_1920,
               AVOIDCHG,
               # health conditions that could be categories
                    # mood/behavior dx
                    K2Q33C,
                    K2Q32C,
                    K2Q34C,
                    # ASD
                    K2Q35C,
                    # brain injury
                    #K2Q46C,
                    # CP
                    K2Q61B,
                    # epilepsy/seizure
                    K2Q42C,
                    # develop delay
                    K2Q36C,
                    # ID
                    K2Q60C,
                    # speach/language dx
                    K2Q37C,
                    # learning disorder
                    K2Q30C,
                #weight
                    FWC_adj)

dat17_18b<-dat17_18%>%
  select(            HHID,FIPSST,STRATUM,
                     InsType_1718,
                        SC_AGE_YEARS,
                    SC_SEX,
                     SC_RACE_R,
                      #   sc_race_ethnic_16to20,
               famstruct5_1718,
               contains("fpl"),
               HHLANGUAGE,
               FAMCOUNT,
               # Child Health Complexity Variables
               HCABILITY,
               HCEXTENT,
               ATHOMEHC,
               ARRANGEHC,
               K4Q22_R,
               K4Q23,
               K4Q24_R,
               K4Q36,
               K4Q01,
               K4Q02_R,
               HOSPITALER,
               K4Q20R,
               BREATHING,
               SWALLOWING,
               STOMACH,
               BLINDNESS,
               K2Q43B,
               PHYSICALPAIN,
               # maybe not use
               HANDS,
               COORDINATION,
               MEMORYCOND,
               WALKSTAIRS,
               DRESSING,
               # other predictors
               C4Q04,
               K5Q20_R,
               K5Q21,
               K8Q35,
               K2Q05,
               MOMAGE,
               StopCutWork_1718,
               AVOIDCHG,
               # health conditions that could be categories
                    # mood/behavior dx
                    K2Q33C,
                    K2Q32C,
                    K2Q34C,
                    # ASD
                    K2Q35C,
                    # brain injury
                    K2Q46C,
                    # CP
                    K2Q61B,
                    # epilepsy/seizure
                    K2Q42C,
                    # develop delay
                    K2Q36C,
                    # ID
                    K2Q60C,
                    # speach/language dx
                    K2Q37C,
                    # learning disorder
                    K2Q30C,
                #weight
                    FWC_adj)

dat16b<-dat16%>%
  select(     HHID,FIPSST,STRATUM,
              instype_16,
                        SC_AGE_YEARS,
            #   sc_age_3cat,
            SC_SEX,
            #   sc_sex,
            SC_RACE_R,
            #SC_RACE_R
            #   sc_race_ethnic_16to20,
               famstruct_16,
               contains("fpl"),
               HHLANGUAGE,
               FAMCOUNT,
               # Child Health Complexity Variables
               HCABILITY,
               HCEXTENT,
               ATHOMEHC,
               ARRANGEHC,
               K4Q22_R,
               K4Q23,
               K4Q24_R,
               K4Q36,
               K4Q01,
               K4Q02_R,
               HOSPITALER,
               K4Q20R,
               BREATHING,
               SWALLOWING,
               STOMACH,
               BLINDNESS,
               K2Q43B,
               PHYSICALPAIN,
               # maybe not use
               HANDS,
               COORDINATION,
               MEMORYCOND,
               WALKSTAIRS,
               DRESSING,
               # other predictors
               C4Q04,
               K5Q20_R,
               K5Q21,
               K8Q35,
               K2Q05,
               MOMAGE,
               StopCutWork_16,
               AVOIDCHG,
               # health conditions that could be categories
                    # mood/behavior dx
                    K2Q33C,
                    K2Q32C,
                    K2Q34C,
                    # ASD
                    K2Q35C,
                    # brain injury
                    K2Q46C,
                    # CP
                    K2Q61B,
                    # epilepsy/seizure
                    K2Q42C,
                    # develop delay
                    K2Q36C,
                    # ID
                    K2Q60C,
                    # speach/language dx
                    K2Q37C,
                    # learning disorder
                    K2Q30C,
                #weight
                    FWC_adj)



```

### Extract these outcome variables from each dataset 
```{r message=FALSE, warning=FALSE}
               #outcomes
#               cg_mentalhealth, cg_mgmtparent,
#               cg_aggravation1, cg_aggravation2, cg_aggravation3,
#               cg_aggravation_comp)
#                # Caregiver, Child, and Family Sociodemographics
#               cg_age_3cat,
#               cg_gender,
#               cg_marital_3cat,
#               cg_education_3cat,
#               cg_relationship_4cat,
```

### Rename the 3 columns named differently to become uniform
```{r warning=FALSE}

detach("package:plyr", unload = TRUE)
dat16b<-dat16b%>%
  rename(instype=instype_16,
         famstruct=famstruct_16,
         StopCutWork=StopCutWork_16)

dat17_18b<-dat17_18b%>%
  rename(instype=InsType_1718,
         famstruct=famstruct5_1718,
         StopCutWork=StopCutWork_1718)

dat19_20b<-dat19_20b%>%
  rename(instype=instype_1920,
         famstruct=famstruct5_1920,
         StopCutWork=StopCutWork_1920)


```

### Combine all 5 years (2016,2017-2018, 2019-2020)
```{r message=FALSE, warning=FALSE}

library(plyr)
dat<-rbind.fill(dat16b,dat17_18b,dat19_20b) #fill non-matching columns with NA




```

### Categorize these vars into 3 groups
```{r message=FALSE, warning=FALSE}

#
#               cg_age_3cat,
#               cg_gender,
#               cg_marital_3cat,
#               cg_education_3cat,
#               cg_relationship_4cat,

#               hcability_3cat,
#               hcextent_3cat,
#               athomehc_3cat,
#               arrangehc_3cat,
               
#               k4q02_r_3cat
#               c4q04_3cat,
#               momage_3cat



dat$AGE_GRP[dat$SC_AGE_YEARS<=4]<-"0-4"
dat$AGE_GRP[dat$SC_AGE_YEARS %in% c(5:8)]<-"5-8"
dat$AGE_GRP[dat$SC_AGE_YEARS %in% c(9:12)]<-"9-12"
dat$AGE_GRP[dat$SC_AGE_YEARS %in% c(13:16)]<-"13-16"
dat$AGE_GRP[dat$SC_AGE_YEARS>=16]<-">16"

dat<-dat%>%
  ## make sure the variables are factors
  mutate(AGE_GRP = factor(AGE_GRP,levels = c("0-4","5-8","9-12","13-16",">16")), 
         SC_SEX = factor(SC_SEX))
```

### Create survey object
```{r message=FALSE, warning=FALSE}

nsch_design<-svydesign(
  id=~HHID,
  strata = ~ STRATUM,
  weights = ~ FWC_adj,
  data = dat)

```

### Free memory
```{r}
#rm(list = c(dat16,dat16b,dat17_18,dat17_18b,dat19_20,dat19_20b))
```


### Descriptive statistics with weight estimates 

### Using SURVYR package and SURVEY package

```{r}
detach("package:plyr", unload = TRUE)
nsch_df_sv<-as_survey(nsch_design)
```


### Creating a subpopulation  
subset(), filter() or even ] can be used on the survey objects to appropriately create sub-population data
```{r}


```


```{r}
nsch_df_sv%>%
  group_by(SC_SEX)%>%
  summarize(N=n(),
            Average_age=survey_mean(SC_AGE_YEARS,vartype = c("ci")),
            pct=survey_prop(prop_method = "likelihood",vartype = c("ci"))) #use Rao Scot Method



```

```{r}
#FLIPPED PYRAMID
library(apyramid)
library(ggplot2)
```

```{r}
## define x-axis limits and labels ---------------------------------------------
## (update these numbers to be the values for your graph)
max_prop <- 30      # choose the highest proportion you want to show 
step <- 5           # choose the space you want between labels 

## this part defines vector using the above numbers with axis breaks
breaks <- c(
    seq(max_prop/100 * -1, 0 - step/100, step/100), 
    0, 
    seq(0 + step / 100, max_prop/100, step/100)
    )

## this part defines vector using the above numbers with axis limits
limits <- c(max_prop/100 * -1, max_prop/100)

## this part defines vector using the above numbers with axis labels
labels <-  c(
      seq(max_prop, step, -step), 
      0, 
      seq(step, max_prop, step)
    )


```

```{r}
## plot the weighted sample population 
weighted_population <- nsch_df_sv %>%
  
  age_pyramid(
    age_group = "AGE_GRP",
    split_by = "SC_SEX", 
    proportion = TRUE) +
  ## only show the x axis label (otherwise repeated in all three plots)
  labs(title = "Weighted sample population", 
       y = "", 
       x = "")  + 
  ## make the x axis the same for all plots 
  scale_y_continuous(
    breaks = breaks, 
    limits = limits, 
    labels = labels)

weighted_population

```



### Generalized linear models
```{r}
#svyglm()

```

### CART using glmertree package

```{r message=FALSE, warning=FALSE}
library(glmertree)
# Regression


# Classification algorithms
```

